### 2020-11-18 paper/sections/experiment.tex
Add selection and parameters

Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
\subsection{Some results}

>>>>

Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
\subsection{Configure Selection}
We simulate the environment with three object detection models, which are SSD ResNet152V1, FasterRCNN ResNet50V1, FasterRCNN InceptionResNetV2. For each model, two kinds of image resolution for inference, which is $1024\times1024$ and $640\times640$, can be picked up. Besides choosing a proper configure of model and image resolution, AutoConfigure needs to select a proper number of frames per second(fps). We in our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. Therefore, the number of actions that the agent can choose is forty-eight.
\subsection{Experiment Parameters}
We apply deep Q-learning policy to train the agent. In the training procedure, we build up eight independently identical environments for each data set to speed up the training and decrease the dependency of the data. The leaning rate is set to 0.001. The discount factor is set to 0.9. For each dataset, we train the agent 10 epochs and 1000 steps per epoch. The exploration factor is 0.9.
\subsection{Some results}
